\section*{Education}
\vspace{-5pt} 
\noindent\rule{\textwidth}{0.4pt} % Horizontal line
% \vspace{0pt}

\subsection*{\textbf{Master of Science in Electrical and Electronics Engineering} \hfill \textit{2022 -- 2024}}  
\noindent\textit{\textbf{International University of Sarajevo}, Sarajevo, Bosnia and Herzegovina} \\
\noindent\textit{\textbf{Graduated with high honors, GPA 3.80/4.00}} 
\begin{itemize}[leftmargin=*,noitemsep,topsep=3pt]
    \item Master's thesis: \enquote{Sensor-less Control of Permanent Magnet Synchronous Motor (PMSM) as a Supplementary Safety Startegy in ASIL D Environment for Electric Vehicles} (July 2024).
    \item Authored a research paper on \enquote{Methods and Applications of Forest Aerial Image Segmentation}, exploring AI-based approaches such as U-Net and R-CNN for processing satellite imagery in forestry applications (May 2023).
    \item Conducted an in-depth research and simulation project on \enquote{Variable Frequency and Variable Voltage Power Supply}, covering power electronics topologies, circuit design, component value calculations, and Simulink based system-level simulations (January 2023).
    \item Authored a research paper titled \enquote{Predicting House Prices Using Advanced Regression Techniques} (December 2022), exploring real estate price prediction using models such as XGBoost, Random Forest, and Artificial Neural Networks (ANN).
\end{itemize}
\vspace{20pt}

\subsection*{\textbf{Bachelor of Science in Electrical and Electronics Engineering} \hfill \textit{2018 -- 2022}\\
Minor in Computer Sciences and Engineering}  
\noindent\textit{\textbf{International University of Sarajevo}, Sarajevo, Bosnia and Herzegovina} \\  
\noindent\textit{\textbf{Graduated with honors, GPA 3.68/4.00}} 
\begin{itemize}[leftmargin=*,noitemsep,topsep=3pt]
    \item Graduation thesis: \enquote{Design and Implementation of an ASIL-D Software Architecture Based on High-Performance FPGA and 32-bit Microcontroller for Automotive Applications} (June 2022).
    \item Software engineering project: \enquote{Generation of PWM Signals Using VHDL to Drive an Electrohydraulic Proportional Valve} (2022).
    \item Designed and built a Bluetooth-controlled four-wheel line follower gripper robot using Arduino (2022).
    \item Created a project management plan for \enquote{Automated Study Gamified Application for Electrical and Electronics Engineering Department} (2021).
    \item Developed a recipe blog web application with full-stack implementation using MongoDB, Node.js, and EJS (2021).
    \item Machine learning project on \enquote{Effects of Life Factors on Studying} using Neural Networks and k-Nearest Neighbors (2020).
    \item Embedded systems project \enquote{Mini Gaming Room}, featuring an LCD mini-game and an LED-based graphical audio/frequency equalizer (2020).
    \item Object-oriented programming project: \enquote{Snake Game} (2020).
    \item Published IEEE paper on \enquote{Slotted Heart-shaped 4.77\,dB Microstrip Coupler} (2020).
    \item Developed a business plan for a pet-sitting company, \enquote{SAME L.L.C.}.
    \item Seminar paper on \enquote{Technology and the Transformation of Work} (2018).
\end{itemize}
\vspace{20pt}

\subsection*{\textbf{First Bosniak High School} \hfill \textit{2018 -- 2022}}  
\noindent\textit{\textbf{First Bosniak Gymnasium}, Sarajevo, Bosnia and Herzegovina} \\
\noindent\textit{\textbf{Graduated with honors, GPA 4.91/5.00}} 
\begin{itemize}[leftmargin=*,noitemsep,topsep=3pt]
    \item Graduation thesis on \enquote{Mechanics of the Human Locomotor System} (2018)
    \item Published seminar paper on \enquote{Graphs of Trigonometric Functions} (2017)
    \item Achieved 6\textsuperscript{th} place in Regional Physics Competition and 21\textsuperscript{st} place in Federal Physics Competition (2017)
\end{itemize}
\vspace{20pt}