\section*{Work Experience}
\vspace{-5pt} 
\noindent\rule{\textwidth}{0.4pt} % Horizontal line
% \vspace{0pt}

\subsection*{\textbf{Automotive Embedded Systems \& Test Engineer} \hfill \textit{August 2022 -- Present}\\ (Hybrid, Full-Time)}  
\noindent\textit{\textbf{Maasu BH d.o.o.}, Sarajevo, Bosnia and Herzegovina} 
\begin{itemize}[leftmargin=*,noitemsep,topsep=3pt]
    \item Worked closely with clients and engineering teams within the German automotive industry, following the V-model development process.
    \item Lead unit \& integration testing of a harvesting robot, developed with Python and ROS in a Linux environment using pytest.
    \item Designed and executed C++ unit tests for electric drive systems in commercial vehicles using Google Test, ensuring robust coverage and compliance with automotive quality standards.
    \item Designed high-level software architecture diagrams and system-level test specifications using Enterprise Architect, based on requirements and use cases.
    \item Authored system-level test specifications and test cases for electric drive software in Codebeamer, ensuring consistency with defined software requirements.
    \item Led the scaling and verification of embedded control software developed in MATLAB Simulink for electric drive systems, utilizing Polyspace and MXAM.
    \item Led and structured four internships within the company, designing their content and framework to align with the company's objectives and ensuring hands-on practical learning experiences for interns.
    \item Led and managed an internal R\&D project as Product Owner and multi-disciplinary engineer (system, hardware, and software) for a custom small-scale autonomous vehicle prototype, contributing to system architecture, technical implementation, and documentation.
    \item Fully designed and developed two custom STM32-based PCBs in KiCad for a small-scale autonomous vehicle: one for interfacing with a BLDC motor controller and inverter for rear-wheel drive, and the other for sensor integration and steering control via a DC motor controller. Scope included schematic design, component selection, PCB layout and routing, Gerber file generation, and managing communication and orders for manufacturing and assembly.
    \item Developed embedded firmware and software in C for the two custom STM32-based PCBs using the STM32Cube environment, HAL library, FreeRTOS, and Micro-ROS. Enabled real-time motor control via on-board motor drivers and sensor data processing, leveraging multi-threading in FreeRTOS and utilizing communication protocols such as I\textsuperscript{2}C, UART, and SPI.
    \item Fully 3D modeled the custom autonomous vehicle in Blender, including 3D printing and the complete manual assembly of both mechanical and electrical components.
\end{itemize}
\vspace{20pt}


\subsection*{\textbf{SoC Design Engineer (Remote, Part-Time)} \hfill \textit{July 2022 -- September 2022}}  
\noindent\textit{\textbf{Chili Chips LLC}, California, USA} 
\begin{itemize}[leftmargin=*,noitemsep,topsep=3pt]
    \item Contributed to the ongoing design and implementation of a custom RISC-V-based processor using SystemVerilog 2017, targeting the GOWIN platform on the Tang Nano 9K FPGA board for educational and embedded applications.
    \item Took part in the development of \textit{eduBOS5}, the first Bosnian educational RISC-V processor, focusing on instruction set architecture and RTL-level design.
    \item Authored and documented technical content for an educational book on low-level processor design, covering HDL fundamentals, RTL design, and hardware development workflows.
    \item Assisted with early-stage simulation and verification of processor modules to validate pipeline behavior and instruction execution logic.
    \item Collaborated remotely with an international team, following best practices in code organization, documentation, and version control.
\end{itemize}
\vspace{20pt}

% \subsection*{
%   \parbox[t]{0.6\textwidth}{\raggedright\textbf{Teaching Assistant -- Programming for Engineers (On-Site, Part-Time)}} \hfill
%   \makebox[0.39\textwidth][r]{\raggedleft\textit{February 2022 -- June 2022}}%
% }
\subsection*{\textbf{Teaching Assistant – Programming for Engineers} \hfill \textit{February 2022 -- May 2022}\\{(On-Site, Part-Time)}} 
\noindent\textit{\textbf{International University of Sarajevo}, Sarajevo, Bosnia and Herzegovina} 
\begin{itemize}[leftmargin=*,noitemsep,topsep=3pt]
    \item Led bi-weekly tutorial sessions for undergraduate students in C and C++, focusing on programming logic and foundational concepts.
    \item Assisted students in understanding low-level programming principles relevant to systems and embedded development.
    \item Created and explained code examples that emphasized structured programming, memory management, and algorithmic thinking.
    \item Provided one-on-one support to students during lab exercises, debugging sessions, and assignments.
    \item Collaborated with the course instructor to ensure alignment between lectures and tutorials, reinforcing key engineering problem-solving skills.
\end{itemize}
\vspace{20pt}


\subsection*{\textbf{IT Intern (Remote, Part-Time)} \hfill \textit{February 2022 -- March 2022}}  
\noindent\textit{\textbf{Energoinvest d.d.}, Sarajevo, Bosnia and Herzegovina} 
\begin{itemize}[leftmargin=*,noitemsep,topsep=3pt]
    \item Gained practical experience with Agile methodologies, including Kanban and writing effective User Stories.
    \item Learned and applied version control using Git for collaborative software development and codebase management.
    \item Contributed to the development of a React-based web application for visualizing air quality data.
    \item Strengthened understanding of the interaction between frontend applications and embedded hardware systems.
    \item Enhanced skills in debugging and testing software modules for data consistency and performance.
\end{itemize}
\vspace{20pt}